---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PokemonAnalyse

<!-- badges: start -->
<!-- badges: end -->

The goal of PokemonAnalyse is to make analysing the "Pokemon" dataset easier

## Installation

You can install the development version of PokemonAnalyse from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PedroDeBos/PokemonAnalyse")
```

## Functions

This package includes 4 functions, which will all be shown including examples below. Important is that all functions rely on the pokemon's name being spelled with a __capital letter__

__pokemon_legendary__: States whether the selected pokemon is legendary or not

```{r example}
library(PokemonAnalyse)
pokemon_legendary("Mewtwo")
pokemon_legendary("Charizard")
```

__pokemon_type__: States the type(s) of the selected pokemon
```{r}
pokemon_type("Groudon")
pokemon_type("Gengar")
```

__pokemon_stats__: Gives a graph of the selected pokemon's stats
```{r, out.height="60%", out.width="60%"}
pokemon_stats("Alakazam")
```

__pokemon_weakness__: Gives a graph of the selected pokemon's weakness'
```{r, out.height="60%", out.width="60%"}
pokemon_weakness("Aggron")
```

## Credits
Pokemon database was taken from Rounak Banik's [kaggle.com](https://www.kaggle.com/datasets/rounakbanik/pokemon) under the CC0 license

Functions were written by Pedro de Bos

