---
title: "pokemonAnalyse"
author: "Pedro de Bos"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pokemonAnalyse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo-FALSE}
library(PokemonAnalyse)
```

## PokemonAnalyse is a mock R-package, created to prove PedroDeBos' ability in creating packages

The package contains a handful of functions to analyse the pokemon database created by Rounak Banik on Kaggle. These functions, pokemon_type, pokemon_stats, pokemon_legendary and pokemon_weakness, help finding specific details about pokemon without having to scan the database yourself.


### Input

Input for all commands is the same, the name of the pokemon who's stats/type/etc. you want to discovered, given as a character to the command. Every pokemon name is required to start with a capital letter. Thus, a command should look like this:

```{r}
pokemon_legendary("Hippowdon")
```

### Output

The commands "pokemon_legendary" and "pokemon_type" both give a string of text as output, as seen below:

```{r}
pokemon_type("Articuno")

pokemon_legendary("Articuno")
```

The commands pokemon_stats and pokemon_weakness both give a plot as output

```{r}
pokemon_stats("Articuno")

pokemon_weakness("Articuno")
```

